% Author        : PokMan Ho pok.ho19@imperial.ac.uk
% Script        : thesis.tex
% Desc          : MRes thesis main tex
% Input         : none
% Output        : pdf thesis in same directory
% Arguments     : 0
% Date          : Jan 2020

\documentclass[a4paper,11pt]{article}
\usepackage[margin=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx, hyperref, longtable, amsmath, amssymb}
\graphicspath{{result/}{../result/}}

\usepackage[
autocite 	= superscript,
backend 	= bibtex,
sortcites 	= true,
style 		= nature
]{biblatex}
\bibliography{../reference/thesis.bib}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue
}

\usepackage{subfiles} %% load last

\newcommand{\As}{\textit{Anabaena sp.}}
\newcommand{\Ct}{\textit{Chroococcidiopsis thermalis}}
\newcommand{\Cs}{\textit{Chroococcidiopsis sp.}}
\newcommand{\Ss}{\textit{Synechocystis sp.}}
\newcommand{\ps}{population size}

\title{MRes thesis}
\author{PokMan Ho}
\date{September 2020}

\begin{document}
\maketitle

\section{Abstract}
\subfile{thesisSec/abstract}

\section{Introduction}
\subfile{thesisSec/intro}

\section{Methodology}
\subfile{thesisSec/method}

\section{Result}
\subfile{thesisSec/res}

\section{Discussion}
\subfile{thesisSec/disc}

\section{Conclusion}
\subfile{thesisSec/conclu}

\section{Acknowledgement}
The author would like to thank \href{mailto:j.rosindell@imperial.ac.uk}{Dr. James Rosindell} and \href{mailto:s.pawar@imperial.ac.uk}{Dr. Samraat Pawar} for accepting this project idea.  Thank you \href{mailto:wei.huang@eng.ox.ac.uk}{Prof. Wei Huang} for agreeing to be the external adviser.  Big thanks to \href{mailto:e.cavan@imperial.ac.uk}{Dr. Emma Cavan} and \href{mailto:t.clegg17@imperial.ac.uk}{Mr. Tom Clegg} for giving great technical helps.

\section{Code and Data availability}
Code scripts are available in respective GitHub \href{https://github.com/ph-u/Project}{repository}.  Parameter, intermediate and final result data files are available on respective Google drive \href{https://drive.google.com/drive/folders/1tp2miPXis7bn-km1THC3ZaRHSRXQGCi5?usp=sharing}{directory}.  Solar station data is freely available on CEDA Archive \href{http://archive.ceda.ac.uk/midas_stations/google_earth/}{website}.  Hourly solar data is available upon request on CEDA Archive \href{https://catalogue.ceda.ac.uk/uuid/220a65615218d5c9cc9e4785a3234bd0}{website}.

\nocite{*}\printbibliography

\section{Appendix}
\subfile{thesisSec/apdx}

\end{document}